---
title: "Rapid Eagle HW2 Exercise I"
output: html_notebook
---

Setup working directory for the rmd file

```{r setup}
library(knitr)
knitr::opts_knit$set(root.dir = 'C:/Users/amit.dingare/Documents/Rapid Eagle/RapidEagleHW2')
#getwd()
```

Read file from the working directory

```{r}
getwd()
refine = read.csv('refine.csv',header=TRUE)
head(refine)
```
1: Clean up brand names
Clean up the 'company' column so all of the misspellings of the brand names are standardized. For example, you can transform the values in the column to be: philips, akzo, van houten and unilever (all lowercase).


## Option 1: Use REGEX
```{r}
refine$company <- gsub("^[Pp].*|^[Ff].*", "philips", refine$company)
refine$company <- gsub("^[Aa].*", "akzo", refine$company)
refine$company <- gsub("^[Vv].*", "van houten", refine$company)
refine$company <- gsub("^[Uu].*", "unilever", refine$company)
```

## Option 2: Use stringdist library

Create a function that replaces every value from the company column with correct
values. We pass two values to the function, a vector of typos and a vector of 
correct values. Then for each value between the typo vector, closeMatch evaluates = string distance between itself and every value of the correct value vector and
creates a weight vector. Then it returns the lowest value from this vector


```{r}
library(stringdist)

closeMatch <- function(x, y) {
  wt <- c()
    for (i in 1:length(y)) {
    wt[i] <- stringdist(x, y[i])
    }
  which.min(wt)
  return(y[which.min(wt)])
}

brandName <- c( "philips", "akzo", "van houten",  "unilever")
refine$company <- sapply(refine$company, closeMatch, y = brandName)
```


# 2: Separate product code and number
```{r}
library(tidyr)
colnames(refine)[which(names(refine) == "Product.code...number")] <- "Productcode_number"
refine <- separate(refine, Productcode_number, c("Productcode", "number"), sep = "-", remove = FALSE)
```

# 3: Add product categories

## Option 1: Use dplyr::inner_join
```{r}
library(dplyr)
Productcode <- c("p", "v", "x", "q")
Productcategory <- c("Smartphone", "TV", "Laptop", "Tablet")
prodCatLookup <- data.frame(Productcode, Productcategory)
refine <- inner_join(refine, prodCatLookup)
```

## Option 2: Use ifelse

This makes a messy implementation. Avoid using sequential ifelses.
```{r}
refine$Productcategory = with(refine,ifelse(Productcode=="p","Smartphone",
                        ifelse(Productcode=="v","TV",                                                   ifelse(Productcode=="x","Laptop",                                               ifelse(Productcode=="q","Tablet","Unknown")))))
```

# 4: Add full address for geocoding

## Option 1: Base R
```{r}
full_address <- paste(refine$address, refine$city, refine$country, sep = ", ")
refine <- cbind(refine, full_address)
```

## Option 2: tidyr::unite
```{r}
refine <- unite(refine, "full_address", address, city, country, sep = ",")
```


# 5: Create dummy variables for company and product category

## Option 1: use base R
```{r}
refine$company_philips = with(refine, ifelse(company=="philips",1,0))
refine$company_akzo = with(refine, ifelse(company=="akzo",1,0))
refine$company_van_houten = with(refine, ifelse(company=="van houten",1,0))
refine$company_unilever = with(refine, ifelse(company=="unilever",1,0))

refine$product_smartphone = with(refine,ifelse(Productcategory=="smartphone",1,0))
refine$product_tv = with(refine,ifelse(Productcategory=="tv",1,0))
refine$product_laptop = with(refine,ifelse(Productcategory=="laptop",1,0))
refine$product_tablet = with(refine,ifelse(Productcategory=="tablet",1,0))
```


## Option 2: use a combination of dplyr::mutate and tidyr::spread
```{r}
refine$company_changed <- paste0("company_",gsub(" ", "_",refine$company))
refine <- refine %>% mutate(flag=1) %>% spread(key = company_changed,value = flag,fill = 0)

refine$Productcategory_changed <- paste0("product_",gsub(" ", "_",refine$Productcategory))
refine <- refine %>% mutate(flag=1) %>% spread(key = Productcategory_changed,value = flag,fill = 0)
```

## Option 3: Use dummies package
```{r}
library(dummies)
company <- gsub(" ", "_",refine$company)
dummy1 <- dummy(company, sep = "_")
refine <- cbind(refine, dummy1)

Product <- gsub(" ", "_",refine$Productcategory)
dummy2 <- dummy(Product, sep = "_")
refine <- cbind(refine, dummy2)
```

Write changed csv

```{r}
write.csv(refine,"refine_changed.csv")
```


